---
title: "R Notebook"
output: html_notebook
---

```{r}
```


```{r}
head(train)
```
```{r}
home_planet_transported <- table(train$HomePlanet, train$Transported)
home_planet_transported_percentage <- prop.table(home_planet_transported, margin =1)

library(ggplot2)

home_planet_result <- as.data.frame.matrix(home_planet_transported_percentage)

home_planet_result$HomePlanet <- rownames(home_planet_result)

home_planet_result_plot <- tidyr::gather(home_planet_result, key = "Transported", value = "Percentage", -HomePlanet)

ggplot(home_planet_result_plot, aes(x = HomePlanet, y = Percentage, fill = Transported)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage * 100)),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  labs(title = "Percentage of Passengers Transported from Each Home Planet")
```
```{r}
cryosleep_percentage <- mean(train$Transported[train$CryoSleep == TRUE], na.rm = TRUE) * 100

pie_data <- data.frame(
  CryoSleep = c("FALSE", "TRUE"),
  Percentage = c(100 - cryosleep_percentage, cryosleep_percentage)
)

ggplot(pie_data, aes(x = "", y = Percentage, fill = CryoSleep)) +
  geom_bar(stat = "identity", width = 1) +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  coord_polar(theta = "y") +
  labs(title = "Percentage of Passengers Transported in Cryo Sleep") +
  theme_void()
```
```{r}
cryosleep_passengers <- subset(train, CryoSleep == TRUE)

cryosleep_passengers$Age_Group <-  cut(cryosleep_passengers$Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+"))

age_counts <- table(cryosleep_passengers$Age_Group)

print(age_counts)
```


```{r}
cryosleep_transported_passengers <- subset(train, CryoSleep == TRUE & Transported == TRUE)

age_counts <- table(cryosleep_transported_passengers$Age_Group)

print(age_counts)

```


```{r}
cryosleep_transported_passengers <- subset(train, CryoSleep == TRUE & Transported == TRUE)

cryosleep_transported_passengers$Age_Group <- cut(cryosleep_transported_passengers$Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+"))

age_counts <- table(cryosleep_transported_passengers$Age_Group)

age_counts_df <- as.data.frame(age_counts)
colnames(age_counts_df) <- c("Age_Group", "Count")

age_counts_df$Percentage <- (age_counts_df$Count / sum(age_counts_df$Count)) * 100

ggplot(age_counts_df, aes(x = Age_Group, y = Percentage, label = sprintf("%.1f%%", Percentage))) +
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(position = position_stack(vjust = 0.5), size = 3) +
  labs(title = "Percentages of Transported Passengers in Cryosleep by Age Group") +
  xlab("Age Group") +
  ylab("Percentage")
```


```{r}
train$Deck <- substr(train$Cabin, 1, 1)

cabin_transported <- table(train$Deck, train$Transported)

cabin_transported_df <- as.data.frame.matrix(cabin_transported)

colnames(cabin_transported_df) <- c("NotTransported", "Transported")

cabin_transported_df$Percentage <- cabin_transported_df$Transported / rowSums(cabin_transported_df) * 100

print(cabin_transported_df)

ggplot(cabin_transported_df, aes(x = rownames(cabin_transported_df), y = Percentage, fill = rownames(cabin_transported_df))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  labs(title = "Percentage of Passengers Transported by Cabin Deck",
       x = "Deck",
       y = "Percentage") +
  theme_minimal()
```


```{r}
age_deck_b_passengers <- subset(train, Deck == "B")

age_deck_b_counts <- table(cut(age_deck_b_passengers$Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+")))

age_deck_b_counts_df <- as.data.frame(age_deck_b_counts)
colnames(age_deck_b_counts_df) <- c("Age_Group", "Count")

total_deck_b_passengers <- nrow(age_deck_b_passengers)
age_deck_b_counts_df$Percentage <- (age_deck_b_counts_df$Count / total_deck_b_passengers) * 100

print(age_deck_b_counts_df)


```


```{r}
age_deck_c_passengers <- subset(train, Deck == "C")

age_deck_c_counts <- table(cut(age_deck_c_passengers$Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+")))

age_deck_c_counts_df <- as.data.frame(age_deck_c_counts)
colnames(age_deck_c_counts_df) <- c("Age_Group", "Count")

total_deck_c_passengers <- nrow(age_deck_c_passengers)
age_deck_c_counts_df$Percentage <- (age_deck_c_counts_df$Count / total_deck_c_passengers) * 100

print(age_deck_c_counts_df)
```


```{r}
cryosleep_deck_b_c_passengers <- subset(train, (Deck == "B" | Deck == "C") & CryoSleep == TRUE)

count_cryosleep_deck_b_c_passengers <- nrow(cryosleep_deck_b_c_passengers)

cat("Number of passengers on decks B and C in CryoSleep:", count_cryosleep_deck_b_c_passengers, "\n")

```


```{r}
total_cryosleep_passengers <- subset(train, CryoSleep == TRUE)
total_cryosleep_passengers_count <- nrow(total_cryosleep_passengers)

cryosleep_deck_b_c_passengers <- subset(train, (Deck == "B" | Deck == "C") & CryoSleep == TRUE)
cryosleep_deck_b_c_passengers_count <- nrow(cryosleep_deck_b_c_passengers)

percentage_cryosleep_deck_b_c <- (cryosleep_deck_b_c_passengers_count / total_cryosleep_passengers_count) * 100

cat("Total percentage of CryoSleep passengers on decks B and C:", percentage_cryosleep_deck_b_c, "%\n")

```


```{r}
train$Side <- substr(train$Cabin, nchar(train$Cabin), nchar(train$Cabin))

side_transported <- table(train$Side, train$Transported)

side_transported_df <- as.data.frame.matrix(side_transported)

colnames(side_transported_df) <- c("NotTransported", "Transported")

side_transported_df$Percentage <- side_transported_df$Transported / rowSums(side_transported_df) * 100

print(side_transported_df)

ggplot(side_transported_df, aes(x = rownames(side_transported_df), y = Percentage, fill = rownames(side_transported_df))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  labs(title = "Percentage of Passengers Transported by Side of the Ship",
       x = "Side",
       y = "Percentage") +
  theme_minimal()


```


```{r}
train$Age_Group <- cut(train$Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+"))

age_transported <- table(train$Age_Group, train$Transported)

age_transported_df <- as.data.frame.matrix(age_transported)

colnames(age_transported_df) <- c("NotTransported", "Transported")

age_transported_df$Percentage <- age_transported_df$Transported / rowSums(age_transported_df) * 100

print(age_transported_df)

library(ggplot2)
ggplot(age_transported_df, aes(x = rownames(age_transported_df), y = Percentage, fill = rownames(age_transported_df))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  labs(title = "Percentage of Passengers Transported by Age Group",
       x = "Age Group",
       y = "Percentage") +
  theme_minimal()
```


```{r}
total_passengers_age <- table(cut(train$Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+")))

total_passengers_age_df <- as.data.frame(total_passengers_age)

colnames(total_passengers_age_df) <- c("Age_Group", "Count")

print(total_passengers_age_df)


```


```{r}
age_0_10_passengers <- subset(train, cut(Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+")) == "0-10")

total_age_0_10_passengers <- nrow(age_0_10_passengers)
transported_age_0_10_passengers <- sum(age_0_10_passengers$Transported == TRUE)

percentage_transported_age_0_10 <- (transported_age_0_10_passengers / total_age_0_10_passengers) * 100

cat("Percentage of Age Group 0-10 passengers transported:", percentage_transported_age_0_10, "%\n")

```


```{r}
age_11_20_passengers <- subset(train, cut(Age, breaks = c(-Inf, 10, 20, 30, 40, 50, 60, 70, Inf), labels = c("0-10", "11-20", "21-30", "31-40", "41-50", "51-60", "61-70", "71+")) == "11-20")

total_age_11_20_passengers <- nrow(age_11_20_passengers)
transported_age_11_20_passengers <- sum(age_11_20_passengers$Transported == TRUE)

percentage_transported_age_11_20 <- (transported_age_11_20_passengers / total_age_11_20_passengers) * 100

cat("Percentage of Age Group 11-20 passengers transported:", percentage_transported_age_11_20, "%\n")
```


```{r}
vip_transported <- table(train$VIP, train$Transported)

vip_transported_df <- as.data.frame.matrix(vip_transported)

colnames(vip_transported_df) <- c("NotTransported", "Transported")

vip_transported_df$Percentage <- vip_transported_df$Transported / rowSums(vip_transported_df) * 100

print(vip_transported_df)

library(ggplot2)
ggplot(vip_transported_df, aes(x = rownames(vip_transported_df), y = Percentage, fill = rownames(vip_transported_df))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  labs(title = "Percentage of VIP Passengers Transported",
       x = "VIP",
       y = "Percentage") +
  theme_minimal()
```


```{r}
destination_transported <- table(train$Destination, train$Transported)

destination_transported_df <- as.data.frame.matrix(destination_transported)

colnames(destination_transported_df) <- c("NotTransported", "Transported")

destination_transported_df$Percentage <- destination_transported_df$Transported / rowSums(destination_transported_df) * 100

print(destination_transported_df)

library(ggplot2)
ggplot(destination_transported_df, aes(x = rownames(destination_transported_df), y = Percentage, fill = rownames(destination_transported_df))) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = sprintf("%.1f%%", Percentage)),
            position = position_stack(vjust = 0.5),
            size = 3, color = "white") +
  labs(title = "Percentage of Passengers Transported by Destination",
       x = "Destination",
       y = "Percentage") +
  theme_minimal()
```


```{r}
total_passengers <- nrow(train)
transported_passengers <- sum(train$Transported == TRUE)

percentage_transported <- (transported_passengers / total_passengers) * 100

cat("Total percentage of passengers transported:", percentage_transported, "%\n")

```


```{r}
Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed